
```{r height, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
```

# Growth charts in JAMES

## Chart naming conventions

The link https://groeidiagrammen.nl/ocpu/lib/james/www/ contains an interactive overview of the available growth charts. There are many different charts: for boys and girls, for preterms, for different age ranges, for specific ethnic groups, for height, weight, BMI, and so on. Each chart has a chart code, a character code identifying the design. This section explains the construction of the chart codes.

The GitHub repository <https://github.com/growthcharts/chartbox> contains the chart libraries that are available to JAMES. The `list_charts()` function produces a tabular overview.

```{r chartlist, eval=TRUE}
charts <- chartbox::list_charts()
dim(charts)
charts[c(1, 22, 23, 300, 301, 340), ]
```

The `chartbox` package currently contains three chart groups: `nl2010`, `preterm` and `who`. Each group collects charts of a similar type. 

| Chart Group | N | Chart code | Description                                     | Source
|:------- | -----:|:---------- |:----------------------------------------------- |:---------
|`nl2010` |   140 | CCCC       | Dutch children 0-21 years, including minorities | @talma2010
|`preterm`|   240 | CCCCCNN    | Dutch preterms, ga <= 36 weeks, 0-4 years       | @bocca2012
|`who`    |    14 | CCCC       | WHO Child Growth Standards 0-4 years            | [WHO](https://www.who.int/childgrowth/en/)

The chart code is an alpha-numeric code of four (for `nl2010` and `who`) or seven (for `preterm`) that uniquely identifies each of the charts. The table below specifies the full coding schema used to construct the chart codes.

| Position | Field      | Value | Description     |
|:----:|:---------- |:----- |:------------------- |
| 1    | Population | N     | Dutch               |
|      |            | T     | Turkish             |
|      |            | M     | Moroccan            |
|      |            | H     | Hindostan           |
|      |            | P     | Preterm             |
|      |            | W     | WHO                 |
|    2 | Sex        | J     | Male                |
|      |            | M     | Female              |
|    3 | Design     | A     | 0-15 months         |
|      |            | B     | 0-4 years, WFH      |
|      |            | C     | 1-21 years          |
|      |            | D     | 0-21 years          |
|      |            | E     | 0-4 years, WFA      |
|    4 | Side       | A     | A4, front           |
|      |            | B     | A4, back            |
|      |            | C     | A4, back, no `hdc`  |
|      |            | D     | square, `dsc`       |
|      |            | H     | square, `hgt`       |
|      |            | O     | square, `hdc`       |
|      |            | Q     | square, `bmi`       |
|      |            | R     | square, `wfh`       |
|      |            | W     | square, `wgt`       |
|      |            | X     | A4, double sided    |
|    5 | Language   | N     | Dutch               |
|      |            | E     | English             |
|  6-7 | Week       | 25-36 | Gestational age     |

For illustration, code `NJAA` references to Dutch (`N`), boys (`J`), 0-15 month (`A`), front side (`A`). Likewise, `PMEAN33` codes for the chart of preterm (`M`), girls (`M`), 0-4 years (`E`), front side (`A`), Dutch language (`N`) born at 33 weeks of gestation (`33`).

Some forms hold multiple growth charts. For example, the `NJAA` chart is designed for A4 paper size (297mm $\times$ 210mm) and contains three growth charts: head circumference by age, length by age, and weight by age. Some others have no diagram, like `NJAB`. All square formats hold just one growth chart. All of the square forms have equal sizes (160mm $\times$ 160mm).

The following table lists the measures per design-form combination. 

| Design | Side  | Measure   | Description
|:------:|:-----:|:--------- |:------------------------------------- |
|    A   |   A   | `hdc`     | Head circumference by age, 0-15 mo    |
|        |       | `hgt`     | Length by age, 0-15 mo                |
|        |       | `wgt`     | Weight by age, 0-15 mo                |
|        |   B   |           | Backside explanations                 |
|        |   D   | `dsc`     | D-score by age, 0-15 mo               |
|        |   H   | `hgt`     | Length by age, 0-15 mo                |
|        |   O   | `hdc`     | Head circumference by age, 0-15 mo    |
|        |   W   | `wgt`     | Weight by age, 0-15 mo                |
|    B   |   A   | `wfh`     | Weight for height, 0-4 yr             |
|        |       | `hgt`     | Length by age, 0-4 yr                 |
|        |   B   | `hdc`     | Head circumference by age, 0-4 yr     |
|        |   C   |           | Backside explanations                 |
|        |   D   | `dsc`     | D-score by age, 0-4 yr                | 
|        |   H   | `hgt`     | Height by age, 0-4 yr                 |
|        |   O   | `hdc`     | Head circumference by age, 0-4 yr     |
|        |   R   | `wfh`     | Weight for height, 0-4 yr             |
|        |   W   | `wgt`     | Weight by age, 0-4 yr                 |
|    C   |   A   | `wfh`     | Weight for height, 1-21 yr            |
|        |       | `hgt`     | height by age, 1-21 yr                |
|        |   B   | `bmi`     | BMI by age, 1-21 yr                   |
|        |       | `hdc`     | Head circumference by age, 1-21 yr    |
|        |   C   | `bmi`     | BMI by age, 1-21 yr                   |
|        |   H   | `hgt`     | Height by age, 1-21 yr                |
|        |   O   | `hdc`     | Head circumference by age, 1-21 yr    |
|        |   Q   | `bmi`     | Body mass index by age, 1-21 yr       |
|        |   R   | `wfh`     | Weight for height, 1-21 yr            |
|    E   |   A   | `wgt`     | Weight by age, 0-4 yr                 |
|        |       | `hgt`     | height by age, 0-4 yr                 |
|        |   B   | `hdc`     | Head circumference by age, 0-4 yr     |
|        |   H   | `hgt`     | Height by age, 0-4 yr                 |
|        |   O   | `hdc`     | Head circumference by age, 0-4 yr     |
|        |   W   | `wgt`     | Weight by age, 0-4 yr                 |

